Predicting Audio Features with Last.fm Tags

### 2023-03-19 paper/main.tex
add bayes parameters table

@@

We configured the boosted tree regressor model with the following training parameters:

\begin{table}[h]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{xgboosttable}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter               & Value \\
      \midrule
      objective               & reg:squarederror  \\
      base score              & 0.5 \\
      booster                 & gbtree  \\
      colsample bylevel       & 1 \\
      colsample bynode        & 1 \\
      colsample bytree        & 1 \\
      gamma\footnotemark[1]   & 0 \\
      learning rate           & 0.300000012 \\
      max delta step          & 0 \\
      max depth               & 6 \\
      min child weight        & 1 \\
      estimators              & 200  \\
      n jobs                  & 12  \\
      num parallel tree       & 1 \\
      predictor               & auto  \\
      random state            & 0 \\
      reg alpha               & 0 \\
      reg lambda              & 1 \\
      scale pos weight        & 1 \\
      subsample               & 2 \\
      tree method             & auto  \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Minimum loss reduction required to make a further partition on a leaf node of the tree.}
      \end{minipage}
      \end{center}
\end{table}

% \begin{table}[h]
% \begin{center}
% \begin{minipage}{\textwidth}
% \caption{Data format for XGBoost regressor}\label{tab2}
% \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcccccc@{\extracolsep{\fill}}}
%       \toprule%
%       & \multicolumn{3}{@{}c@{}}{Tags as columns\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Tokens as columns\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
%       Track & rock &  \dots  & $\y_{valence}$ & $\position_{0} &  \dots $ & $\sigma_{valence}$ \\
%       \midrule
%       Element 3  & 100 &  \dots  & 0.563 & 780 A & 1166 & $1239\pm100$\\
%       Element 4  & 75  &  \dots  & 0.434 & 900 A & 1268 & $1092\pm40$\\
%       \botrule
%       \end{tabular*}
%       \footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
%       \footnotetext[1]{Example for a first table footnote.}
%       \footnotetext[2]{Example for a second table footnote.}
% \end{minipage}
% \end{center}
% \end{table}

>>>>

% JAIME: For 1e-10 notation
\usepackage{siunitx}

@@

We configured the boosted tree regressor model with the training parameters listed in table \ref{table_xgboost_training_params}.

\begin{table}[h]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{table_xgboost_training_params}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter               & Value \\
      \midrule
      objective               & reg:squarederror  \\
      base score              & 0.5 \\
      booster                 & gbtree  \\
      colsample bylevel       & 1 \\
      colsample bynode        & 1 \\
      colsample bytree        & 1 \\
      gamma\footnotemark[1]   & 0 \\
      learning rate           & 0.300000012 \\
      max delta step          & 0 \\
      max depth               & 6 \\
      min child weight        & 1 \\
      estimators              & 200  \\
      n jobs                  & 12  \\
      num parallel tree       & 1 \\
      predictor               & auto  \\
      random state            & 0 \\
      reg alpha               & 0 \\
      reg lambda              & 1 \\
      scale pos weight        & 1 \\
      subsample               & 2 \\
      tree method             & auto  \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Minimum loss reduction required to make a further partition on a leaf node of the tree.}
      \end{minipage}
      \end{center}
\end{table}

\subsection{Naive Bayes Regressor}

The Naive Bayes Regressor, and in particular, Bayesian Ridge, is the model used for regression in this case.

% COMMENT copied FROM BayesianRidge source code
% https://github.com/scikit-learn/scikit-learn/blob/9aaed4987/sklearn/linear_model/_bayes.py#L24
%
%     There exist several strategies to perform Bayesian ridge regression. This 
%     implementation is based on the algorithm described in Appendix A of
%     (Tipping, 2001) where updates of the regularization parameters are done as
%     suggested in (MacKay, 1992). Note that according to A New
%     View of Automatic Relevance Determination (Wipf and Nagarajan, 2008) these
%     update rules do not guarantee that the marginal likelihood is increasing
%     between two consecutive iterations of the optimization.

The training parameters are listed in table \ref{table_bayesian_training_params}.

\begin{table}[h]
      \begin{center}
      \begin{minipage}{174pt}
      \caption{Training parameters for XGBoost regressor}\label{table_bayesian_training_params}%
      \begin{tabular}{@{}llll@{}}
      \toprule
      Parameter                     & Value \\
      \midrule
      Maximum iterations            & 300   \\
      Tolerance\footnotemark[1]     & \num{1e-03} \\
      alpha 1                       & \num{1e-06} \\
      alpha 2                       & \num{1e-06} \\
      lambda 1                      & \num{1e-06} \\
      lambda 2                      & \num{1e-06} \\
      \botrule
      \end{tabular}
      \footnotetext[1]{Tolerance for the stopping criteria.}
      \end{minipage}
      \end{center}
\end{table}

\subsection{Fine-tuned Transformer}
